---
title: '6306 DDS: Case Study 1'
author: "Jaclyn Ann Coate & Huy Hoang Nguyen"
date: "10/7/2019"
output: html_document
---

# Prep Environment
```{r}
library(tidyverse)
library(ggthemes)
library(plyr)
library(dplyr)
```

# 1. How many breweries are present in each state?

## Import data Breweries into R
```{r}
breweries <- read.csv("https://raw.githubusercontent.com/BivinSadler/MDS-6306-Doing-Data-Science-Fall-2019/master/Unit%208%20and%209%20Case%20Study%201/Breweries.csv", header = TRUE)
breweries
nrow(breweries)
summary(breweries)
```

## Graph breweries by state
```{r}
breweries %>% ggplot(mapping = aes(x=State, fill=State)) +
  geom_bar(sstat = "identity") +
  #theme_excel_new() +
  theme_tufte() +
ggtitle("Breweries by State") + ylab("Count") + xlab("State")
```

#Jaclyn Completed:
#### Created reproducible import code for Huy and Jaclyn to be able to reproduce on their local computers.
#### Added nrow and ggplot to properly graph and answer question 1

#Huy To Do: 
#### Huy: Add lables to the top of every bar in the chart above.
#### Huy: Remove colored labels from the graph.



# 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.  (RMD only, this does not need to be included in the presentation or the deck.)

## Import Beers data
```{r}
beers <- read.csv("https://raw.githubusercontent.com/BivinSadler/MDS-6306-Doing-Data-Science-Fall-2019/master/Unit%208%20and%209%20Case%20Study%201/Beers.csv", header = TRUE)
str(beers)
```

## Observe that ID on beers - Brewery_id and and breweries - Brew_ID  - we rename by Brew_ID
```{r}
beers <- rename(beers, Brew_ID = Brewery_id)
beers
```

## Rename "Name" in breweries by "Name_Brew" and "Name" in beers by "Name_Beer"
```{r}
breweries <- rename(breweries, Name_Brew = Name)
beers <- rename(beers, Name_Beer = Name)

breweries
beers
```

## Complete full_join of both data frames to loose minimum amount of data
```{r}
brew.beer <- full_join(breweries, beers, by = "Brew_ID")
str(brew.beer)
brew.beer
```

## Print first 6 and last 6 rows of merged data set
```{r}
brew.beer %>% tail(6)
brew.beer %>% head(6)
```

#Jaclyn Completed:
#### Created reproducible import code for Huy and Jaclyn to be able to reproduce on their local computers.
#### Read through and added 'evaluation' code lines for completed data sets
#### Added "tail" and "head" code to to satisfy the question requirements

#Huy Completed: 
#### Column rename of "key": "Brew_ID"
#### Full join merge between tables


# 3. Address the missing values in each column.
```{r}
brew.beer %>% summarise_all(funs(sum(is.na(.))))
```
## Only ABV 62NA and IBU 1005NA
#### Huy: Should we add anyhting here for 'addressing' the NAs? Should we drop them? Should we talk more about them?


# 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

## We will create 2 df for ABV not NA and IBU not NA - we dont want 1 df for both because we loose a lot of data - if we considerABV,... only 62 deleted and IBU
```{r}
brew.beer.cleanABV <- brew.beer %>% filter(!is.na(ABV))
MedianABV <- brew.beer.cleanABV %>% group_by(State) %>% summarise(medABV = median(c(ABV)))
MedianABV %>% ggplot(aes(fill=State, y=medABV, x=State)) + geom_bar(stat="identity") + 
  theme_excel_new() +
ggtitle("Median ABV by State") + ylab("ABV") + xlab("State")

brew.beer.cleanIBU <- brew.beer %>% filter(!is.na(IBU))
MedianIBU <- brew.beer.cleanIBU %>% group_by(State) %>% summarise(medIBU = median(c(IBU)))
MedianIBU %>% ggplot(aes(fill=State, y=medIBU, x=State)) + geom_bar(stat="identity") + 
  theme_excel_new() +
ggtitle("Median IBU by State") + ylab("IBU") + xlab("State")
```
#### Huy: Can we clean up these bar charts a little bit? They seem crowded. I've added a theme, labels, and titles for clarity. Can you remove the colored key and add lables to the top of each state?



# 5a. Which state has the maximum alcoholic (ABV) beer? 
## Huy: I am a little confused here. He's asking for the max ABV not the max median. Shouldn't we take this from the original merged data set and not the median calculation?
```{r}
y_maxABV <- max(MedianABV[,2])
y_maxABV
stateABV_associated <- MedianABV[MedianABV$medABV == y_maxABV, "State"]
stateABV_associated
```

# 5b. Which state has the most bitter (IBU) beer?
## Huy: I am a little confused here. He's asking for the max Bitter not the max median IBU. Shouldn't we take this from the original merged data set and not the median calculation?
```{r}
y_maxIBU <- max(MedianIBU[,2])
y_maxIBU
stateIBU_associated <- MedianIBU[MedianIBU$medIBU == y_maxIBU, "State"]
stateIBU_associated
```





# 6. Comment on the summary statistics and distribution of the ABV variable.
```{r}
summary(MedianABV)
```



# 7a. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? 
# 7b. Draw a scatter plot.  
# 7c. Make your best judgment of a relationship and EXPLAIN your answer.
```{r}
```

```{r}
```

```{r}
```
