---
title: "EDA Presentation"
author: "Jaclyn Ann Coate & Huy Hoang Nguyen"
date: "`r Sys.Date()`"
output: 
  revealjs::revealjs_presentation:
    transition: slide
    theme: simple
    highlight: pygments
    center: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_knit$set(root.dir = "..")
knitr::include_graphics("/Users/Jaco/Desktop/SMU/DS_6306_Doing_Data_Science/Unit_8_9_CaseStudy1")
```

# Contributors
## Huy Hoang Nguyen
- Data Cruncher
- Hype Crew

## Jaclyn Ann Coate
- Architect
- Visualization Lover

```{r Prepare the environment}
library(tidyverse)
library(ggthemes)
library(dplyr)
library(highcharter)
library(ggmap)
library(ggExtra)
library(treemapify)
library(maps)
library(naniar)
library(knitr)
library(revealjs)
```

# Review
## Data
- We utilized R for our data crunching an analysis
- We choose to do analyses on ABV and IBU on separate data sets
- We are excited to show you our findings!

```{r Import Brewery data into R}
breweries <- read.csv("https://raw.githubusercontent.com/BivinSadler/MDS-6306-Doing-Data-Science-Fall-2019/master/Unit%208%20and%209%20Case%20Study%201/Breweries.csv", header = TRUE, strip.white=TRUE)
#str(breweries)
#nrow(breweries)
#summary(breweries)
#glimpse(breweries)
```

```{r Import map data from highcharter}
mapdata <- get_data_from_map(download_map_data("countries/us/us-all"))
#glimpse(mapdata)
```

```{r Table and data frame number of breweries by state, rename column to code for join statement}
#glimpse(breweries)
breweryGeo <- data.frame(table(breweries$State))
colnames(breweryGeo) <- c("code", "Breweries")
breweryGeo$StateNam <- state.name[match(breweryGeo$code, state.abb)]
#glimpse(breweryGeo)
```

```{r Drop NAs and categorize the columns corrently}
breweryGeo <- filter(breweryGeo, !is.na(code))
#glimpse(breweryGeo)

breweryGeo$Breweries <- as.numeric(breweryGeo$Breweries)
breweryGeo$State <- as.character(breweryGeo$code)
#glimpse(breweryGeo)

#glimpse(breweryGeo)
#str(breweryGeo)
```

# Brewery Geo Distribution
## Breweries by State
```{r}
colBreweries <- hcmap("countries/us/us-all", data = breweryGeo, value = "Breweries",
      joinBy = c("hc-a2", "code"),
      title = "Breweries by State",
      name = "Number of Breweries",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list()
      )

hc_colorAxis(colBreweries, min = 1,
            max = 50,
            #type = 'logarithmic',
            minColor = '#f1ccc7',
            maxColor = '#a83b2a',
            lineColor = 'black',
            lineWidth = .5
            )
```

```{r Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.(RMD only, this does not need to be included in the presentation or the deck.)}
beers <- read.csv("https://raw.githubusercontent.com/BivinSadler/MDS-6306-Doing-Data-Science-Fall-2019/master/Unit%208%20and%209%20Case%20Study%201/Beers.csv", header = TRUE)
#str(beers)
#glimpse(beers)
```

```{r We obvserve that our key value "Brew_ID" from our breweries data is named "Brewery_id". In order to have these column names match and make tables easier to merge we remane the column in the beer data set.}
beers <-  beers %>% dplyr::rename( Brew_ID = Brewery_id)
#glimpse(beers)
```

```{r We observe that two "name" columns exist between the data sets. So we assign them unique column names by data set.}
breweries <- breweries %>% dplyr::rename(Name_Brew = Name)  
beers <- beers %>% dplyr::rename(Name_Beer = Name)

#glimpse(breweries)
#glimpse(beers)
```

```{r We complete a full_join of both data frames to loose minimum amount of data for review.}
brew.beer <- full_join(breweries, beers, by = "Brew_ID")
#str(brew.beer)
#glimpse(brew.beer)
```

```{r We print first 6 and last 6 rows of merged data set below.}
#brew.beer %>% head(6)
#brew.beer %>% tail(6)
```



```{r ABV: Create Median ABV Data Set}
brew.beer.cleanABV <- brew.beer %>% filter(!is.na(ABV))
```

```{r ABV: roup median ABV by State}
brew.beerABV <- aggregate(brew.beer.cleanABV$ABV, by=list(brew.beer.cleanABV$State), FUN = median)
#glimpse(brew.beerABV)
```

```{r ABV: Label Columns}
colnames(brew.beerABV) <- c("State", "MedABV")
#glimpse(brew.beerABV)
```

```{r ABV: Turn ABV into percent which is standard format for ABV}
brew.beerABV <- mutate(brew.beerABV, ABVper = MedABV * 100)
#glimpse(brew.beerABV)
```

```{r ABV: Sort data for column graph}
brew.beerABV <- brew.beerABV[order(brew.beerABV$MedABV),]
```

```{r ABV: Retain sorted order in the Plot}
brew.beerABV$State <- factor(brew.beerABV$State, levels = brew.beerABV$State)
```

# Alcohol by Volume (ABV) Analysis
## Median ABV by State
```{r ABV: geom_bar chart of median ABV by State}
brew.beerABV %>% ggplot(mapping = aes(x=State, y=MedABV))  +
  geom_bar(stat = "identity", fill = "dark green") +
  theme_excel_new() + 
  theme(legend.position="none", axis.text.x = element_text(angle=65, vjust=0.1)) +
  ggtitle("Median ABV by State") + ylab("ABV") + xlab("State") 
```

```{r ABV: Create key column for geo map to reference}
brew.beerABV$code <- brew.beerABV$State

#glimpse(brew.beerABV)
#summary(brew.beerABV)
#nrow(brew.beerABV)
```

## Median ABV by State
```{r ABV: hc geo map of Median ABV by State}
colorABV <- hcmap("countries/us/us-all", data = brew.beerABV, value = "ABVper",
      joinBy = c("hc-a2", "code"), name = "ABV",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 2, valueSuffix = "%")
      )

hc_colorAxis(colorABV, min = 3,
            max = 7,
            #type = 'logarithmic',
            minColor = '#ffffff',
            maxColor = '#003400',
            lineColor = 'black',
            lineWidth = .5
            )
```

```{r ABV: Max ABV by State}
#glimpse(brew.beer)
maxABV <- data.frame(brew.beer[which.max(brew.beer$ABV),])
#maxABV
```

```{r ABV: into percent which is normal format for ABV}
maxABV <- mutate(maxABV, ABVper = ABV * 100)
#maxABV
```

```{r ABV: key column for geo map to reference}
maxABV$code <- maxABV$State
```

## Highest ABV
### Colorado at 12.8%
```{r ABV: Geo map of Colorado, fig.width = 7, fig.height = 5}
colorMaxABV <- hcmap("countries/us/us-all", data = maxABV, value = "ABVper",
      joinBy = c("hc-a2", "code"), name = "ABV",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 1, valueSuffix = "%"))

hc_colorAxis(colorMaxABV, min = 3,
            max = 7,
            #type = 'logarithmic',
            minColor = '#003400',
            maxColor = '#003400',
            lineColor = 'black',
            lineWidth = .5
            )
```

## ABV Distribution
- 75% of the ABV falls between 5.5% - 5.8%
- Higher than Budweiser's 4.2%
```{r ABV: Boxplot of Median ABV distribution, fig.width = 7, fig.height = 5}
MedianABV <- brew.beer.cleanABV %>% group_by(State) %>% summarise(medABV = median(c(ABV)))
#summary(MedianABV)

MedianABV %>% ggplot(mapping = aes(y = medABV)) +
  geom_boxplot(fill = "dark green", color = "black") +
  theme_excel_new() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("Median ABV Summary Statistics") + ylab("Median ABV") + xlab("")
```


```{r IBU: Create Median IBU Data Set}
brew.beer.cleanIBU <- brew.beer %>% filter(!is.na(IBU))
```

```{r IBU: Group median IBU by State}
brew.beerIBU <- aggregate(brew.beer.cleanIBU$IBU, by=list(brew.beer.cleanIBU$State), FUN = median)
#glimpse(brew.beerIBU)
```

```{r IBU: Label Columns}
colnames(brew.beerIBU) <- c("State", "MedIBU")
#glimpse(brew.beerIBU)
```

```{r OBU: Sort data for column graph}
brew.beerIBU <- brew.beerIBU[order(brew.beerIBU$MedIBU),]
```

```{r IBU: Retain sorted order in the Plot}
brew.beerIBU$State <- factor(brew.beerIBU$State, levels = brew.beerIBU$State)
```

# Bitterness (IBU) Analysis
## Median IBU by State
```{r geom_bar chart of median IBU by State}
brew.beerIBU %>% ggplot(mapping = aes(x=State, y=MedIBU)) +
  geom_bar(stat = "identity", fill = "dark blue") +
  theme_excel_new() +
  theme(legend.position="none", axis.text.x = element_text(angle=65, vjust=0.6)) +
  ggtitle("Median IBU by State") + ylab("IBU") + xlab("State")
```

```{r Create key column for geo map to reference}
brew.beerIBU$code <- brew.beerIBU$State
#glimpse(brew.beerIBU)
#summary(brew.beerIBU)
#nrow(brew.beerIBU)
```

```{r Adding South Dakota 0 so it renders on GEO map even with a 0 value}
sd <- data.frame("SD", 0, "SD")
colnames(sd) <- c("State", "MedIBU", "code")
#sd
brew.beerIBU <- rbind(brew.beerIBU, sd)
```

```{r IBU: Create key column for geo map to reference}
breweryGeo <- data.frame(table(breweries$State))
colnames(breweryGeo) <- c("code", "Breweries")
```

## Median IBU by State
```{r IBU: hc geo map of Median IBU by State}
#glimpse(brew.beerIBU)
colorIBU <- hcmap("countries/us/us-all", data = brew.beerIBU, value = "MedIBU",
      joinBy = c("hc-a2", "code"), name = "IBU",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 1)) 

hc_colorAxis(colorIBU, min = 18,
            max = 62,
            #type = 'logarithmic',
            minColor = '#ffffff',
            maxColor = '#000080',
            lineColor = 'black',
            lineWidth = .5
            )
```

```{r Max IBU by State}
#glimpse(brew.beer)
maxIBU <- data.frame(brew.beer[which.max(brew.beer$IBU),])
#maxIBU
```

```{r key column for geo map to reference}
maxIBU$code <- maxIBU$State
```

## Highest IBU
### Oregon at 138
```{r Geo map of Oregon, fig.width = 7, fig.height = 5}
colorMaxIBU <- hcmap("countries/us/us-all", data = maxIBU, value = "IBU",
      joinBy = c("hc-a2", "code"), name = "IBU",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 1))

hc_colorAxis(colorMaxIBU, min = 18,
            max = 62,
            #type = 'logarithmic',
            minColor = '#ffffff',
            maxColor = '#000080',
            lineColor = 'black',
            lineWidth = .5
            )
```



## IBU Distribution

- 75% of the IBU falls between 30 - 43
- Higher than Budweiser's 7
```{r Boxplot of Median IBU distribution, fig.width = 7, fig.height = 5}
brew.beer.cleanIBU <- brew.beer %>% filter(!is.na(IBU))
MedianIBU <- brew.beer.cleanIBU %>% group_by(State) %>% summarise(medIBU = median(c(IBU)))
#summary(MedianIBU)

MedianIBU %>% ggplot(mapping = aes(y = medIBU)) +
  geom_boxplot(fill = "dark blue", color = "black") +
  theme_excel_new() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("Median IBU Summary Statistics") + ylab("Median IBU") + xlab("")
```

# ABV and IBU Correlation
## ABV v IBU
- Positive correlation
- No confirmed causation
```{r Scatter plot with densigram, fig.width = 10, fig.height = 5}
#brew.beer
ggMarginal(brew.beer %>% ggplot(mapping = aes(x=IBU, y=ABV)) +
  geom_point() + 
  geom_smooth(method = 'lm') +
  theme_excel_new() +
ggtitle("Bitterness (IBU) vs. Alcoholic Content (IBV)") + ylab("IBU") + xlab("ABV"), type = "densigram", fill = "blue")
```

## ABV v IBU by State
```{r Scatter plot of IBU vs ABV By State}
#brew.beer
hchart(brew.beer, "scatter", hcaes(x = IBU, y = ABV, group = State)) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Bitterness (IBU) vs. Alcoholic Content (IBV)")
```