library(knitr)
---
title: "Key for HTML"
author: "Jaclyn Ann Coate"
date: "10/20/2019"
output:
    ioslides_presentation:
      df_print: paged
#output:
#  powerpoint_presentation:
#    df_print: paged
    
#output:
#  reveal_js::revealjs_presentation:
#   df_print: paged
#   theme:moon
#   transition: zoom
---

```{r]

```

# section header
## subsection header
### subsubsection header

*italic*

**bold**

***bold italic***

- bullet

-bullet
  -bullet

* bullet
  * bullet
    * bullet
    
- Chapter 4 is all about presetnations
#"https://bookdown.org/yihui/rmarkdown/"








```{r set up, include = FALSE}
#knitr options
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warn = FALSE)
knitr::opts_chunk$set(message = FALSE)
# set root directory to project root

knitr::opts_knit$set(root.dir = "..")

```

```{r}

# ignores root.dir, have to type the full relative path
#knitr::include_graphics(#home/david/project/images/)

#need to have a root directory from where everything is going ot pull from then use the location of that image of on your computer
```












