---
title: "Case Study 1: Final Presentation"
author: "Jaclyn Coate & Huy Hoang Nguyen"
date: "`r Sys.Date()`"
output: 
  revealjs::revealjs_presentation:
    transition: slide
    keep_md: true
    theme: simple
    highlight: pygments
    center: true
    css: styles.css
    includes:
      in_header: backgroundsilver.html
    self_contained: false
    reveal_plugins: ["chalkboard"]
    reveal_options:
      chalkboard:
        theme: whiteboard
        toggleNotesButton: false
---

```{r setup, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::include_graphics("/Users/Jaco/Desktop/SMU/DS_6306_Doing_Data_Science/Unit_8_9_CaseStudy1/presentations")
```

```{r Introduction}
# As data scientists for Budweiser we were thrilled to help decide on new release beers that will compete with the booming microbrewery growth in the United States. This review will contain an analysis of beer bitterness (or IBU) and alcohol by volume (or ABV) by state. This will lead into our recommendations for new beer releases by regional market in the US. We expect Budweiser to be able to compete and excel in this rapidly expanding sector.
```

```{r Prepare the environment}
library(tidyverse)
library(ggthemes)
library(dplyr)
library(highcharter)
library(ggmap)
library(ggExtra)
library(treemapify)
library(maps)
library(naniar)
library(knitr)
library(revealjs)
library(htmltools)
library(viridisLite)
library(treemap)
library(RColorBrewer)
library(class)
library(caret)
library(VIM)
library(lattice)
library(mice)
```

# Budweiser an InBev Company {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
## Budweiser {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- Microbrewery Analysis
- Recommended beer releases for microbrewery market entry

# Contributors {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
## Huy Hoang Nguyen {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- Data Cruncher
- Hype Crew

## Jaclyn Coate {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- Architect
- Visualization Lover

```{r Import Brewery data into R}
breweries <- read.csv("https://raw.githubusercontent.com/BivinSadler/MDS-6306-Doing-Data-Science-Fall-2019/master/Unit%208%20and%209%20Case%20Study%201/Breweries.csv", header = TRUE, strip.white=TRUE)
#str(breweries)
#nrow(breweries)
#summary(breweries)
#glimpse(breweries)
```

```{r Import map data from highcharter}
mapdata <- get_data_from_map(download_map_data("countries/us/us-all"))
#glimpse(mapdata)
```

```{r Table and data frame number of breweries by state, rename column to code for join statement}
#glimpse(breweries)
breweryGeo <- data.frame(table(breweries$State))
colnames(breweryGeo) <- c("code", "Breweries")
breweryGeo$StateNam <- state.name[match(breweryGeo$code, state.abb)]
#glimpse(breweryGeo)
```

```{r Drop NAs and categorize the columns corrently}
breweryGeo <- filter(breweryGeo, !is.na(code))
#glimpse(breweryGeo)

breweryGeo$Breweries <- as.numeric(breweryGeo$Breweries)
breweryGeo$State <- as.character(breweryGeo$code)
#glimpse(breweryGeo)

#glimpse(breweryGeo)
#str(breweryGeo)
```

# Brewery Geo Distribution {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
## Breweries by State {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 1}
colBreweries <- hcmap("countries/us/us-all", data = breweryGeo, value = "Breweries",
      joinBy = c("hc-a2", "code"),
      title = "Breweries by State",
      name = "Number of Breweries",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list()
      )

hc_colorAxis(colBreweries, min = 1,
            max = 50,
            #type = 'logarithmic',
            minColor = '#f1ccc7',
            maxColor = '#a83b2a',
            lineColor = 'black',
            lineWidth = .5
            )
```

```{r}
# In the above geo map we can tell there is a large distribution of breweries throughout the United States. California, Colorado, Michigan, and Oregon are all some of the leaders in microbreweries in the US. Texas gets an honorable mention and is not close behind.  
```

```{r Question 2: Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.}
beers <- read.csv("https://raw.githubusercontent.com/BivinSadler/MDS-6306-Doing-Data-Science-Fall-2019/master/Unit%208%20and%209%20Case%20Study%201/Beers.csv", header = TRUE)
#str(beers)
#glimpse(beers)
```

```{r We obvserve that our key value "Brew_ID" from our breweries data is named "Brewery_id". In order to have these column names match and make tables easier to merge we remane the column in the beer data set.}
beers <-  beers %>% dplyr::rename( Brew_ID = Brewery_id)
#glimpse(beers)
```

```{r We observe that two "name" columns exist between the data sets. So we assign them unique column names by data set.}
breweries <- breweries %>% dplyr::rename(Name_Brew = Name)  
beers <- beers %>% dplyr::rename(Name_Beer = Name)

#glimpse(breweries)
#glimpse(beers)
```

```{r We complete a full_join of both data frames to loose minimum amount of data for review.}
brew.beer <- full_join(breweries, beers, by = "Brew_ID")
#str(brew.beer)
#glimpse(brew.beer)
```

```{r Question 2: We print first 6 and last 6 rows of merged data set below.}
invisible(brew.beer %>% head(6))
invisible(brew.beer %>% tail(6))
```

```{r Question3: ABV: Create Median ABV Data Set}
brew.beer.cleanABV <- brew.beer %>% filter(!is.na(ABV))
```

```{r ABV: roup median ABV by State}
brew.beerABV <- aggregate(brew.beer.cleanABV$ABV, by=list(brew.beer.cleanABV$State), FUN = median)
#glimpse(brew.beerABV)
```

```{r ABV: Label Columns}
colnames(brew.beerABV) <- c("State", "MedABV")
#glimpse(brew.beerABV)
```

```{r ABV: Turn ABV into percent which is standard format for ABV}
brew.beerABV <- mutate(brew.beerABV, ABVper = MedABV * 100)
#glimpse(brew.beerABV)
```

```{r ABV: Sort data for column graph}
brew.beerABV <- brew.beerABV[order(brew.beerABV$MedABV),]
```

```{r ABV: Retain sorted order in the Plot}
brew.beerABV$State <- factor(brew.beerABV$State, levels = brew.beerABV$State)
```

# Alcohol by Volume (ABV) Analysis {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 4: ABV: geom_bar chart of median ABV by State, results = "hide"}
brew.beerABV %>% ggplot(mapping = aes(x=State, y=ABVper))  +
  geom_bar(stat = "identity", fill = "dark green") +
  theme_excel_new() + 
  theme(legend.position="none", axis.text.x = element_text(angle=65, vjust=0.1)) +
  ggtitle("Median ABV by State") + ylab("ABV") + xlab("State") 
```

```{r ABV: Create key column for geo map to reference}
brew.beerABV$code <- brew.beerABV$State

#glimpse(brew.beerABV)
#summary(brew.beerABV)
#nrow(brew.beerABV)
```

## Median ABV by State {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 4: ABV: hc geo map of Median ABV by State}
colorABV <- hcmap("countries/us/us-all", data = brew.beerABV, value = "ABVper",
      joinBy = c("hc-a2", "code"), name = "ABV",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 2, valueSuffix = "%")
      )

hc_colorAxis(colorABV, min = 3,
            max = 7,
            #type = 'logarithmic',
            minColor = '#ffffff',
            maxColor = '#003400',
            lineColor = 'black',
            lineWidth = .5
            )
```

```{r}
# In reviewing our bar chart of Median ABV by state, you can see that there is not a lot of variation in median ABV when comparing state to state. This tells us that while there may be some high ABVs present, normally most breweries fall within a relatively narrow range. To further show this closeness in Median ABV, we see here our geo map does not have a large range in gradient color.
```

```{r Question 5: ABV: Max ABV by State}
#glimpse(brew.beer)
maxABV <- data.frame(brew.beer[which.max(brew.beer$ABV),])
#maxABV
```

```{r ABV: into percent which is normal format for ABV}
maxABV <- mutate(maxABV, ABVper = ABV * 100)
#maxABV
```

```{r ABV: key column for geo map to reference}
maxABV$code <- maxABV$State
```

## Highest ABV {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
### Colorado at 12.8% {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 5: ABV: Geo map of Colorado, fig.width = 7, fig.height = 5}
 colorMaxABV <- hcmap("countries/us/us-all", data = maxABV, value = "ABVper",
      joinBy = c("hc-a2", "code"), name = "ABV",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 1, valueSuffix = "%"))

 hc_colorAxis(colorMaxABV, min = 3,
            max = 7,
            #type = 'logarithmic',
            minColor = '#003400',
            maxColor = '#003400',
            lineColor = 'black',
            lineWidth = .5
            )
```

## ABV Distribution & Summary{data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
#### 75% of the ABV falls between 5.5% - 5.8%
#### Higher than Budweiser's 4.2%
```{r Question 6: ABV: Boxplot of Median ABV distribution, fig.width = 7, fig.height = 5}
MedianABV <- brew.beer.cleanABV %>% group_by(State) %>% summarise(medABV = median(c(ABV)))
MedABVper <- mutate(MedianABV, ABVper = medABV * 100)
#summary(MedianABV)

MedABVper %>% ggplot(mapping = aes(y = ABVper)) +
  geom_boxplot(fill = "dark green", color = "black") +
  theme_excel_new() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("Median ABV Distribution") + ylab("Median ABV") + xlab("ABV")
```

```{r}
# In reviewing this boxplot, we can see our Median ABV distribution is small. The majority of the beers (75%) that are produced fall between 5.5% - 5.8%.  This is slightly higher than the mass-produced Budweiser products of 4.2%. Whenever local consumers are given an option, they are likely to choose a microbrew that contains a slightly higher ABV than Budweiser’s traditional products. For this reason, we will be recommending new Budweiser releases by region of a different ABV than what Budweiser is used to.
```

```{r Question3: IBU: Create Median IBU Data Set}
brew.beer.cleanIBU <- brew.beer %>% filter(!is.na(IBU))
```

```{r IBU: Group median IBU by State}
brew.beerIBU <- aggregate(brew.beer.cleanIBU$IBU, by=list(brew.beer.cleanIBU$State), FUN = median)
#glimpse(brew.beerIBU)
```

```{r IBU: Label Columns}
colnames(brew.beerIBU) <- c("State", "MedIBU")
#glimpse(brew.beerIBU)
```

```{r OBU: Sort data for column graph}
brew.beerIBU <- brew.beerIBU[order(brew.beerIBU$MedIBU),]
```

```{r IBU: Retain sorted order in the Plot}
brew.beerIBU$State <- factor(brew.beerIBU$State, levels = brew.beerIBU$State)
```

# Bitterness (IBU) Analysis {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 4: geom_bar chart of median IBU by State, results = "hide"}
brew.beerIBU %>% ggplot(mapping = aes(x=State, y=MedIBU)) +
  geom_bar(stat = "identity", fill = "dark blue") +
  theme_excel_new() +
  theme(legend.position="none", axis.text.x = element_text(angle=65, vjust=0.6)) +
  ggtitle("Median IBU by State") + ylab("IBU") + xlab("State")
```

```{r Create key column for geo map to reference}
brew.beerIBU$code <- brew.beerIBU$State
#glimpse(brew.beerIBU)
#summary(brew.beerIBU)
#nrow(brew.beerIBU)
```

```{r Adding South Dakota 0 so it renders on GEO map even with a 0 value}
sd <- data.frame("SD", 0, "SD")
colnames(sd) <- c("State", "MedIBU", "code")
#sd
brew.beerIBU <- rbind(brew.beerIBU, sd)
```

```{r IBU: Create key column for geo map to reference}
breweryGeo <- data.frame(table(breweries$State))
colnames(breweryGeo) <- c("code", "Breweries")
```

## Median IBU by State {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 4: IBU: hc geo map of Median IBU by State}
#glimpse(brew.beerIBU)
colorIBU <- hcmap("countries/us/us-all", data = brew.beerIBU, value = "MedIBU",
      joinBy = c("hc-a2", "code"), name = "IBU",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 1)) 

hc_colorAxis(colorIBU, min = 18,
            max = 62,
            #type = 'logarithmic',
            minColor = '#ffffff',
            maxColor = '#000080',
            lineColor = 'black',
            lineWidth = .5
            )
```

```{r}
# We can tell from our gradient geo map that the median IBU varies greatly between states. There are a lot of beers with many different measure for this characteristic of beer. Unlike ABV (which falls in a smaller range), IBU has a lot of possibilities for the new release beers for Budweiser.
```

```{r Question 5: Max IBU by State}
#glimpse(brew.beer)
maxIBU <- data.frame(brew.beer[which.max(brew.beer$IBU),])
#maxIBU
```

```{r key column for geo map to reference}
maxIBU$code <- maxIBU$State
```

## Highest IBU {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
### Oregon at 138 {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 5: Geo map of Oregon, fig.width = 7, fig.height = 5}
colorMaxIBU <- hcmap("countries/us/us-all", data = maxIBU, value = "IBU",
      joinBy = c("hc-a2", "code"), name = "IBU",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 1))

hc_colorAxis(colorMaxIBU, min = 18,
            max = 62,
            #type = 'logarithmic',
            minColor = '#ffffff',
            maxColor = '#000080',
            lineColor = 'black',
            lineWidth = .5
            )
```

## IBU Distribution & Summary{data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
#### 75% of the IBU falls between 30 - 43
#### Higher than Budweiser's 7
```{r Question 6: Boxplot of Median IBU distribution, fig.width = 7, fig.height = 5}
brew.beer.cleanIBU <- brew.beer %>% filter(!is.na(IBU))
MedianIBU <- brew.beer.cleanIBU %>% group_by(State) %>% summarise(medIBU = median(c(IBU)))
#summary(MedianIBU)

MedianIBU %>% ggplot(mapping = aes(y = medIBU)) +
  geom_boxplot(fill = "dark blue", color = "black") +
  theme_excel_new() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ggtitle("Median IBU Distribution") + ylab("Median IBU") + xlab("")
```

```{r}
# IBU is measured on a scale from 1 to 100. This scale measures the amount of isomerizes alpha acids in a beer. In general, the standard IBU of Budweiser is 7. When we review the above plots, we can see the range of median IBU level in beer produced by microbreweries is around 30-43 (75%). These medians are higher than the IBU of Budweiser. For this reason, we recommend that new Budweiser release beers will be higher in IBU than the traditional products.
```

# ABV & IBU Correlation {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 7: Scatter plot with densigram, fig.width = 10, fig.height = 5, results = "hide"}
#brew.beer
brew.beerABVper <- mutate(brew.beer, ABVper = ABV * 100)
#glimpse(brew.beerABVper)

ggMarginal(brew.beerABVper %>% ggplot(mapping = aes(x=IBU, y=ABVper)) +
  geom_point() + 
  geom_smooth(method = 'lm') +
  theme_excel_new() +
ggtitle("Bitterness (IBU) vs Alcoholic Content (IBV)") + ylab("IBU") + xlab("ABV"), type = "densigram", fill = "blue")
```

```{r Creating R]regional data column based on State}
#glimpse(brew.beerABVper)
brew.beerABVper$Region[brew.beerABVper$State == "ME"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "NH"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "VT"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "MA"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "RI"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "CT"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "NY"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "NJ"] <- "Northeast"
brew.beerABVper$Region[brew.beerABVper$State == "PA"] <- "Northeast"

brew.beerABVper$Region[brew.beerABVper$State == "ND"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "SD"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "NE"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "KS"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "MN"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "IA"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "MO"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "WI"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "IL"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "IN"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "MI"] <- "Midwest"
brew.beerABVper$Region[brew.beerABVper$State == "OH"] <- "Midwest"

brew.beerABVper$Region[brew.beerABVper$State == "OK"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "TX"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "AR"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "LA"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "MS"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "KY"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "TN"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "AL"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "FL"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "GA"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "SC"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "NC"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "VA"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "WV"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "MD"] <- "South"
brew.beerABVper$Region[brew.beerABVper$State == "DE"] <- "South"

brew.beerABVper$Region[brew.beerABVper$State == "WA"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "OR"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "CA"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "AK"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "HI"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "AZ"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "NV"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "ID"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "MT"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "WY"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "CO"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "NM"] <- "West"
brew.beerABVper$Region[brew.beerABVper$State == "UT"] <- "West"
#glimpse(brew.beerABVper)
```

## ABV vs IBU by Region {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Scatter plot of IBU vs ABV By Region}
#glimpse(brew.beerABVper)
hchart(brew.beerABVper, "scatter", hcaes(x = IBU, y = ABVper, group = Region)) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Bitterness (IBU) vs Alcoholic Content (IBU)")
```

## ABV vs IBU Summary {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- Positive correlation
- No confirmed causation
```{r}
# There is a relationship between IBU and ABV. Based on this scatter plot and correlation line we can see a positive linear relationship. In general, we can confirm that when the ABV of a beer rises so will its IBU.
```

# Beer Styles by Region {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r}
# Question 9: Here we will complete a full analysis of median IBU, average ABV, and popular style by region. We will then have a list of new beer releases by style and a range of IBU and ABVs that should be targeted moving forward by Budweiser in order to compete in the microbrewery market.
```

## Top 5 Beer Styles in the South {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r SOUTH: Top Beer types in South data manipulation}
#glimpse(brew.beerABVper)
brew.beerSO <- filter(brew.beerABVper, Region == "South")
#brew.beerSO

beer.typeSO <- data.frame(table(brew.beerSO$Style))
#glimpse(beer.typeSO)
colnames(beer.typeSO) <- c("Type", "Count")
beer.typeSO$Type <- as.character(beer.typeSO$Type)
beer.typeSO$Count <- as.numeric(beer.typeSO$Count)
#glimpse(beer.typeSO)

#view(beer.typeSO)
topSOtype <- data.frame(beer.typeSO %>% top_n(5))
#view(topSOtype)
```

```{r Treemap of top beer styles in the South}
hctreemap2(topSOtype, group_vars = "Type", 
           size_var = "Count", color_var = "Count"
           ) %>% 
  hc_colorAxis(minColor = brewer.pal(7, "Reds")[1],
               maxColor = brewer.pal(7, "Reds")[7]) %>%
  hc_title(text = "Top 5 Beer Styles in the South")
```

```{r Will need to add a South regional column to combine data}
list2.1 <- 1:5
list2.2 <- rep("South",length(list2.1))
topSOtype <- cbind(topSOtype, list2.2)
colnames(topSOtype) <- c("Type", "Count", "Region")
topSOtype$Region <- as.character(topSOtype$Region)
#glimpse(topSOtype)
```

## Top 5 Beer Styles in the Midwest {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r MIDWEST: Top Beer types in Midwest data manipulation}
#glimpse(brew.beerABVper)
brew.beerMW <- filter(brew.beerABVper, Region == "Midwest")
#brew.beerMW

beer.typeMW <- data.frame(table(brew.beerMW$Style))
#glimpse(beer.typeMW)
colnames(beer.typeMW) <- c("Type", "Count")
beer.typeMW$Type <- as.character(beer.typeMW$Type)
beer.typeMW$Count <- as.numeric(beer.typeMW$Count)
#glimpse(beer.typeMW)

#view(beer.typeMW)
topMWtype <- data.frame(beer.typeMW %>% top_n(5))
#view(topMWtype)
```

```{r Treemap of top beer styles in the Midwest}
hctreemap2(topMWtype, group_vars = "Type", 
           size_var = "Count", color_var = "Count"
           ) %>% 
  hc_colorAxis(minColor = brewer.pal(7, "Greys")[1],
               maxColor = brewer.pal(7, "Greys")[7]) %>%
  hc_title(text = "Top 5 Beer Styles in the Midwest")
```

```{r Will need to add a Midwest regional column to combine data}
list3.1 <- 1:5
list3.2 <- rep("Midwest",length(list3.1))
topMWtype <- cbind(topMWtype, list3.2)
colnames(topMWtype) <- c("Type", "Count", "Region")
topMWtype$Region <- as.character(topMWtype$Region)
#glimpse(topMWtype)
```

## Top 5 Beer Styles in the West {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r WEST: Top Beer types in West data manipulation}
#glimpse(brew.beerABVper)
brew.beerWE <- filter(brew.beerABVper, Region == "West")
#brew.beerWE

beer.typeWE <- data.frame(table(brew.beerWE$Style))
#glimpse(beer.typeWE)
colnames(beer.typeWE) <- c("Type", "Count")
beer.typeWE$Type <- as.character(beer.typeWE$Type)
beer.typeWE$Count <- as.numeric(beer.typeWE$Count)
#glimpse(beer.typeWE)

#view(beer.typeWE)
topWEtype <- data.frame(beer.typeWE %>% top_n(5))
#view(topWEtype)
```

```{r Treemap of top beer styles in the West}
hctreemap2(topWEtype, group_vars = "Type", 
           size_var = "Count", color_var = "Count"
           ) %>% 
  hc_colorAxis(minColor = brewer.pal(7, "Blues")[1],
               maxColor = brewer.pal(7, "Blues")[7]) %>%
  hc_title(text = "Top 5 Beer Styles in the West")
```

```{r Will need to add a West regional column to combine data}
list4.1 <- 1:5
list4.2 <- rep("West",length(list3.1))
topWEtype <- cbind(topWEtype, list3.2)
colnames(topWEtype) <- c("Type", "Count", "Region")
topWEtype$Region <- as.character(topWEtype$Region)
#glimpse(topWEtype)
```

## Top 5 Beer Styles in the Northeast {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r NORTHEAST: Top Beer types in Northeast data manipulation}
#glimpse(brew.beerABVper)
brew.beerNE <- filter(brew.beerABVper, Region == "Northeast")
#brew.beerNE

beer.typeNE <- data.frame(table(brew.beerNE$Style))
#glimpse(beer.typeNE)
colnames(beer.typeNE) <- c("Type", "Count")
beer.typeNE$Type <- as.character(beer.typeNE$Type)
beer.typeNE$Count <- as.numeric(beer.typeNE$Count)
#glimpse(beer.typeNE)

#view(beer.typeNE)
topNEtype <- data.frame(beer.typeNE %>% top_n(5))
#view(topNEtype)
```

```{r Treemap of top beer styles in the Northeast}
hctreemap2(topNEtype, group_vars = "Type", 
           size_var = "Count", color_var = "Count"
           ) %>% 
  hc_colorAxis(minColor = brewer.pal(7, "Oranges")[1],
               maxColor = brewer.pal(7, "Oranges")[7]) %>%
  hc_title(text = "Top 5 Beer Styles in the Northeast")
```

```{r Will need to add a Northwest regional column to combine data}
list1.1 <- 1:5
list1.2 <- rep("Northeast",length(list1.1))
topNEtype <- cbind(topNEtype, list1.2)
colnames(topNEtype) <- c("Type", "Count", "Region")
topNEtype$Region <- as.character(topNEtype$Region)
#glimpse(topNEtype)
```

## Regional Style Summary {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- Very common trend among styles by region
- Only 6 different beer style favorites between all 4 regions

# Top 6 Beer Styles in the US {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
## Top 6 Beer Styles in the US {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Combining all type of beer by region dataframes for full view}
topTypeRegion <- rbind(topMWtype, topSOtype, topNEtype, topWEtype)
#view(topTypeRegion)
```

```{r Treemap of top beer styles in the US}
hctreemap2(topTypeRegion, group_vars = "Type", 
           size_var = "Count", color_var = "Count") %>%
  hc_colorAxis(minColor = brewer.pal(7, "Greens")[1],
               maxColor = brewer.pal(7, "Greens")[7]) %>%
  hc_title(text = "Top 6 Beer Styles in the US")
```

# ABV & IBU by Region {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
## Average ABV by Region {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Mean ABV by region data manipulation}
#glimpse(brew.beerABVper)
#view(brew.beerABVper)
bbABVper.clean <- brew.beerABVper %>% filter(!is.na(brew.beerABVper$ABVper))

#bbABVper.clean
bbABVper.cleanmea <- aggregate(bbABVper.clean$ABVper, by=list(bbABVper.clean$Region), FUN = mean)
colnames(bbABVper.cleanmea) <- c("Region", "MeanABV")
bbABVper.cleanmea$MeanABV <- round(bbABVper.cleanmea$MeanABV, 2)
#bbABVper.cleanmea
```

```{r Bar chart of Mean ABV by Region}
hchart(bbABVper.cleanmea, "column", hcaes(x = Region, y = MeanABV)) %>% 
  hc_title(text = "Average ABV by Region") %>%
  hc_add_theme(hc_theme_google())
```

## Median IBU by Region {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Median IBU by region data manipulation}
#glimpse(brew.beerABVper)
#view(brew.beerABVper)
bbIBU.clean <- brew.beerABVper %>% filter(!is.na(brew.beerABVper$IBU))

#bbIBU.clean
bbIBU.cleanmed <- aggregate(bbIBU.clean$IBU, by=list(bbIBU.clean$Region), FUN = median)
colnames(bbIBU.cleanmed) <- c("Region", "MedianIBU")
#bbIBU.cleanmed

#bbIBU.clean
bbIBU.cleanmea <- aggregate(bbIBU.clean$IBU, by=list(bbIBU.clean$Region), FUN = mean)
colnames(bbIBU.cleanmea) <- c("Region", "MeanIBU")
#bbIBU.cleanmea
```

```{r Bar chart of Median IBU by Region}
hchart(bbIBU.cleanmed, "column", hcaes(x = Region, y = MedianIBU)) %>% 
  hc_title(text = "Median IBU by Region") %>%
  hc_add_theme(hc_theme_google())
```

# Data Review {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r Question 8}
# We have performed a full k-nearest neighbor (KNN) analysis on our data. In order to do this, we have identified, classified, and imputed the missing data in order to keep from losing over half of our data set after our full join. This has allowed us to have more confidence in our model.
```

```{r Classification of missing data}
invisible(pMiss <- function(x){sum(is.na(x))/length(x)*100})
invisible(apply(brew.beer,2,pMiss))
invisible(apply(brew.beer,1,pMiss))
```

## Histogram & Pattern of Missing Data {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r <Helpful visual representation> aggrmake, results = "hide"}
aggr.brew.beer <- aggr(brew.beer, labels=names(brew.beer),
                        cex.axis=.7, gap=3, ylab=c("Histogram of Missing Data","Pattern"))
#marginplot(brew.beer[,c("ABV","IBU")])
```

## Missing Data Pattern {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
```{r}
md.pattern(brew.beer)
```

```{r  Imputing the missing data, results="hide"}
invisible(brew.beer.impute <- mice(brew.beer[,c("Beer_ID","ABV","IBU")],m=5,maxit=50,meth='pmm',seed=100))
#summary(brew.beer.impute)
invisible(brew.beer.impute$imp$ABV) #check the imputed data ABV
invisible(brew.beer.impute$imp$IBU) # check the imputed data IBU
invisible(brew.beer.draft <- complete(brew.beer.impute,1))  # Complete impute dataset
#view(brew.beer.draft)
```

```{r Create new dataset after imputing the missing data}
brew.beer.draft <- brew.beer.draft %>% dplyr::rename(ABV.New = ABV)
brew.beer.draft <- brew.beer.draft %>% dplyr::rename(IBU.New = IBU)
brew.beer.New <- full_join(brew.beer, brew.beer.draft, by = "Beer_ID")
#view(brew.beer.New)
#styles <- unique(brew.beer.New$Style)
#view(styles)
```

```{r Create 2 dataframes  - IPA and Ales and regroup them, results = "hide"}
Ales.beer <- cbind(brew.beer.New, type='Ales', stringsAsFactors=F) %>% filter(grepl('\\bale\\b', Style, ignore.case=T))
IPA.beer <- cbind(brew.beer.New, type='IPA', stringsAsFactors=F) %>% filter(grepl('\\bIPA\\b', Style, ignore.case=T))
IPA.Ales <- union(Ales.beer, IPA.beer)
IPA.Ales$type <- as.factor(IPA.Ales$type)
```

```{r KNN model, results = "hide"}
set.seed(5)
splitPerc = .7
iterations = 250
numks = 100 
masterAcc = matrix(nrow = iterations, ncol = numks)
for(j in 1:iterations) {
  accs = data.frame(accuracy = numeric(numks), k = numeric(numks))
  trainIndices = sample(1:dim(IPA.Ales)[1],round(splitPerc * dim(IPA.Ales)[1]))
  train = IPA.Ales[trainIndices,]
  test = IPA.Ales[-trainIndices,]
  for(i in 1:numks) {
    classifications = knn(train[,c('IBU.New','ABV.New')],test[,c('IBU.New','ABV.New')],as.factor(train$type), prob = TRUE, k = i)
    table(as.factor(test$type),classifications)
    CM = confusionMatrix(table(as.factor(test$type),classifications))
    masterAcc[j,i] = CM$overall[1]
  }
}
MeanAcc = colMeans(masterAcc)
invisible(plot(seq(1,numks,1),MeanAcc, type = "l"))
k <- which.max(MeanAcc)
```

```{r The best value of k is 11 for %Acurracy, results = "hide"}
classifications = knn(train[,c('IBU.New','ABV.New')],test[,c('IBU.New','ABV.New')],train$type, prob = TRUE, k)
invisible(table(test$type,classifications))
invisible(confusionMatrix(table(test$type,classifications)))
```

## K Nearest Neighbors Model {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- 77% Confidence
- 75% - 82% Confidence Interval
```{r}
# In running a 250-iteration model we are able to have 77% confidence we can classify competitors’ beers on the market based on their IBU and ABV characteristics. We have obtained a confidence interval of 75%-82%. If we use the 11 closest beers to compare (nearest neighbors) we have a 75-82% chance of categorizing the beer correctly as an Ale or IPA.

# We would have liked to see above 85% and since we are only seeing 77 we will continue our investigation with the omitted NA data instead of incorporating into our final data for drawing our conclusions.
```

# Final Recommendations & Summary {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
## New Release Beer Charactersitics {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
## Styles {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- IPA
- Pale Ale
- Amber
- Blonde Ale
- Double IPA
- Pale Wheat Ale
```{r}
# Above are the recommended special release styles to be rotated by region in the US. Through our data analysis it was determined that there were not large differences in the most popular styles in the US today. Taking advantage of the cost effectiveness of only releasing 6 different styles of beer will be crucial. Making sure they are released in different regions will promote scarcity - which will in turn create demand.
```

## ABV & IBU Ranges {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- ABV: 5.8 - 6.0%
- IBU: 20 - 40
```{r}
# Above are the recommended ranges of ABV and IBU for the special release beers.
```

## In Closing {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}
- Scarcity creates demand
- Beers tailored by region
- Competitive ranges of ABV and IBU
```{r}
# Part of the hype surrounding microbrewery releases in the US is that the beers are not easily attainable. Budweiser can use this to their advantage by having limited releases by region. Only one or two of the recommended styles at a time. Also making sure that they are only available for a limited time.

# In our analysis we were able to surface a popular range of ABV and IBU for Budweiser’s new release beers. Breweries are releasing a higher ABV than the standard Budweiser brand. These new release beers will compete with those higher ABV brands. We are moving forward with Budweiser releasing any of the above mentioned styles with a range of 5.8%-6.0% ABV.

# During our IBU review we noticed that IBU is quite higher than the traditional Budweiser brands. For this reason, we chose to only recommend a new IBU on the lower side of the range. This is to prevent alienating any of our traditional customers and still allow these new release beers to be palatable for everyone. Moving forward we advise that Budweiser offer their new releases styles with IBUs that range between 20-40 IBU.
```

# Thank You {data-background="https://i.ibb.co/M6Yh3pg/In-Bev-Background.png"}